Language-Based Security for Low-Level MPC

### 2024-05-14 ppdp24/example-bdoz.tex
checkpoint

The full protocol for malicious secure product of secrets $x$ (that
is, $\elab{\secret{x}}{1}$) and $y$ (that is, $\elab{\secret{y}}{2}$)
using Beaver triple $a,b,c$ is defined in Figure \ref{fig-bdoz}. Both
parties interact in secure opening of $x \fplus a$ and $y + b$,
followed by local computation to compute their share of the $x * y$
using only local addition and product as per standard protocol
\cite{XXX}. The non-interactive reconstruction of the local authentication
key for both the secure openings and the final reveal is enabled by the
semi-homorphic properties of the BDOZ scheme.

>>>>

The full protocol for malicious secure product of secrets $x$ (that
is, $\elab{\secret{x}}{1}$) and $y$ (that is, $\elab{\secret{y}}{2}$)
using Beaver triple $a,b,c$ is defined in Figure \ref{fig-bdoz}. Both
parties interact in secure opening of $x \fplus a$ and $y + b$,
followed by the non-interactive computation of shares of $x * y$
for secure reveals as per standard protocol
\cite{XXX}. The non-interactive reconstruction of the local authentication
key for both the secure openings and the final reveal is enabled by the
semi-homorphic properties of the BDOZ scheme.
